detect patches

### 2024-01-26 scripts/classify_patches.Rmd
fn to subset patches - tweaking aggregation factors for 10-20 mins per spp

p <- '../results/suitability_maps'
f <- file.path(p, list.files(p, pattern = '1k-'))
info <- lapply(f, file.info)

info1 <- info[[1]]$size/1e9

gd <- '/media/steppe/hdd/Geospatial_data'
hydr_bound <- rast( file.path(gd, 'WBD_rast', 'hu10R-line.tif') )
hydr_ftr <-  rast( file.path(gd, 'river_resistance', 'water_ftR.tif') )

@@

  # read in file
  r <- rast(x)
  taxon <- gsub('1k.*$', '', basename(x))
  pout <- '../results/patches'
  fsize <- file.info(f[1])$size/1e9

@@

  if(fsize < 0.2){r1 <- r} else
    if(fsize < 0.4){r1 <- terra::aggregate(r, 2, fun = 'mean')} else 
      if(fsize < 0.7){r1 <- terra::aggregate(r, 3, fun = 'mean')} else
        {r1 <- terra::aggregate(r, 4, fun = 'mean')}

@@

lapply(f, patcheR)

>>>>

p <- '../results/suitability_maps'
f <- file.path(p, list.files(p, pattern = '1k-'))

gd <- '/media/steppe/hdd/Geospatial_data'
hydr_bound <- rast( file.path(gd, 'WBD_rast', 'hu10R-line.tif') )
hydr_ftr <-  rast( file.path(gd, 'river_resistance', 'water_ftR.tif') )
rm(gd)

@@

  # read in file
  r <- rast(x)
  taxon <- gsub('1k.*$', '', basename(x))
  pout <- '../results/patches'
  fsize <- file.info(x)$size/1e9

@@

  if(fsize < 0.3){r1 <- terra::aggregate(r, 2, fun = 'mean')} else
    if(fsize < 0.5){r1 <- terra::aggregate(r, 3, fun = 'mean')} else 
      if(fsize < 0.7){r1 <- terra::aggregate(r, 4, fun = 'mean')} else
        if(fsize > 0.9){r1 <- terra::aggregate(r, 5, fun = 'mean')}

@@

lapply(f[4:355], patcheR) # start 9:05
